DRAFT: Towards a paper on patient movement in the Victorian hospital system

### 2025-05-06 reports/report.qmd
pre-qin edits

Beyond simple models, there is vanishingly small possibility of finding tractable analystical expressions for the hitting times.

## Experimental Setup

>>>>

Beyond simple models, there is vanishingly small possibility of finding computable analytical expressions for the hitting times.
Instead we examine the empirical distributions from simulating the dynamics.
To do this, we iterate over all facilities, seeding 30 individuals in that single facility, and simulating until a fixed end time, using a discrete-time Markov Chain formulation.
We note the number of individuals in each facility at each time step.
The central metric we will examine is the hitting time.
In these experiments, to e

## Results

```{python}

```

Plotting the aggregated hitting times as an empirical cumulative distribution function (ECDF) in @fig-ecdf, we can see that

### 2025-05-06 reports/sketch.qmd
small edit: small analytical example
small content adds
pre-qin edits

plt.xlim(-5, 370)
plt.ylim(-0.01, 0.15)

@@

@@

>>>>

#plt.plot(ana_E_hitT_naive, np.linspace(0, 1, len(ana_E_hitT_naive)), 
#         label='naive\nanalytical', linestyle='dashed')

plt.xlim(-5, 500)
plt.ylim(-0.01, 0.2)

@@

# plt.savefig("early_time_ecdf.png", dpi=360)
```

@@

Examining the deviations greater than 1.0, we see they are all edges that are self-loops of a particular location. This occurs due to the rate of indirect departures being greater than 1, which is a byproduct of our location size estiamtion procedure. 
```{python}
from echidna import graph_importer as gim

# investigating the weirdness in the RHS
investigation_location = 8386

tempo = gim.make_graph(str(root / "data/concordant_networks/temponet_14_365.lgl"))
investi_locs = tempo.vs.select(loc_eq=investigation_location)
self_loops = tempo.es.select(_from_in=investi_locs, _to_in=investi_locs)
sloop_source_times = [edge.source_vertex['time'] for edge in self_loops]
sloop_target_times = [edge.target_vertex['time'] for edge in self_loops]
self_loop_df = pl.DataFrame({
  'source_time': sloop_source_times, 
  'target_time': sloop_target_times,
  'weight': self_loops['weight'],
})
